---
title: "Assignment1"
output: word_document
---

ASSIGNMENT	#1		
1. What  are the different steps	of data	analysis	and what is done during	 each step.

Problem definition and planning

The starting point for data analysis is a data set which contains the measured  or collected data values represented as numbers or text. The business unit has to decide on objectives for the data science teams. These objectives usually require significant data collection and analysis. We need a measurable way to know if the business is advancing toward its goals. Key metrics or performance indicators must be identified early in the process.

Preparing data

Pre-processing/Data preparation involves merging data into a table by integrating the data from multiple sources. Once the data is in a tabular format, it should be fully characterized. The data should be cleaned by resolving ambiguities and errors, removing redundant and problematic data, and eliminating columns of data irrelevant to the analysis.

Data Analysis

In this step data is studied to build an intuition for the data. Data is viewed from different perspectives. Calculate basic summary descriptive statistics on data. You need to learn the shape, size, type and general layout of the data that you have.

Deployment

In this step we present the final results.


2. What	are the	different ways to create a vector in R?
  
  First Method : Using c() function:
  
```{r tidy = FALSE}
  
  v1<-c(1,2,3,4,5)
  print(v1)
  
```
  
  Second method using range: 
  
```{r}
  v2<-1:5
  v3<-2:-2
  v2
  v3
```
  
  Third Method: Using seq()
  
```{r}
  v4<-seq(1,5,by=2)
  v5<-seq(1,5,length.out = 3)
  v4
  v5
```
  
 Fourth method: Using rep()
 
```{r} 
  v6<-rep(1:3,4)
  v7<-rep(c(1,3,2),each=4)
  v6
  v7
```

3. Create the following	vector and check the class ('x','x','x',1,3,5,7,9,2,4,6,8,10)

```{r}
   v8<-c('x','x','x',1,3,5,7,9,2,4,6,8,10)
   class(v8)
```

   
4. Create a vector of positive odd integers less than 100.
 
```{r}
   v9<-seq(1,100,2)
   v9
```
   
5. Remove the values greater than 60 and less than 80
  
```{r}
  V9<-v9[!(v9>60 & v9<80)]
  V9
```
   
6. Write a function to return standard deviation, mean and median of the vector.
   Verify with example.
   
```{r}
   sdmm<-function(v10){
     return(list(SD=sd(v10),Mean=mean(v10),Median=median(v10)))
   }
   
   x<-sdmm(c(1,2,3,4,5))
   print(x)
```

7. Create two matrices	of the form from the given set	of numbers} in 
Two ways X1	= {2,3,7,1,6,2,3,5,1} and	x2={3,2,9,0,7,8,5,8,2}

```{r}
x1<-c(2,3,7,1,6,2,3,5,1)
x2<-c(3,2,9,0,7,8,5,8,2)
```
First Way:

```{r tidy = FALSE}
M1<-matrix(x1,3)
M2<-matrix(x2,3)
M2
```
Second way:

```{r tidy = FALSE}
M3<-matrix(x1,3,byrow=TRUE)
M4<-matrix(x2,3,byrow=TRUE)
M3
```
8. Find	the matrix product.

```{r tidy = FALSE}
M5<-M1%*%M2
M5

M6<-M3%*%M4
M6
```

9. Find	the class of 'iris'	dataframe, find the class of all the columns of 'iris'	
Get the	summary. Get rownames, column names. Get the number  of rows and number of columns.

```{r}
class(iris)
class(colnames(iris))
summary(iris)
rownames(iris)
colnames(iris)
length(rownames(iris))
length(colnames(iris))
```
OR
```{r}
dim(iris)
```

10. Get	the last	two rows in the	last 2 columns from iris dataset.
    ```{r}
    iris[149:150,4:5]
    ```
